Is It Drift?

### 2021-08-30 graphs_newt_snakes/is_it_drift.Rmd
I looked at the interaction between the differece between snake and newt phenotypes and the amount of newts and snakes killed. I got a strange result and am wondering why? I also started the selection coefficients rmarkdown. I want to see if there is a corelation between phenotype and survibility.

var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE){

@@

 combo <- rbind(data_frame_newt, data_frame_snake)
 combo_s <- combo[sample(nrow(combo), nrow(combo)), ]

p <- ggplot(combo_s) +
  #xlim(0, 1000)+
    ggtitle(title, subtitle = subt) +
    xlab(x_label) + ylab(y_label)+
    geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color=type), alpha=0.1)+
    scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
    theme(plot.title = element_text(size=5)) +
    theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
  if(logy==TRUE){
    p = p + scale_y_log10()
  }
  return(p)

@@

>>>>

var_by_var <- function(Newt_file_x, Snake_file_x, Newt_file_y, Snake_file_y, title, subt, x_label, y_label, logy=FALSE, subtract_x=FALSE){

@@

 if(subtract_x==FALSE){
   combo <- rbind(data_frame_newt, data_frame_snake)
   combo_s <- combo[sample(nrow(combo), nrow(combo)), ]
   p <- ggplot(combo_s) +
    #xlim(0, 1000)+
      ggtitle(title, subtitle = subt) +
      xlab(x_label) + ylab(y_label)+
      geom_point(aes(x=as.numeric(value_x), y=as.numeric(value_y), color=type), alpha=0.1)+
      scale_color_manual(name = "Species", values = c("Newt" = "darkred", "Snake" = "steelblue"))+
      theme(plot.title = element_text(size=5)) +
      theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
 }
 if(subtract_x==TRUE){
    subtract_val <- data_frame_snake_x$value_x - data_frame_newt_x$value_x
    total_sub_dataframe <- data.frame(subtract_val, data_frame_newt_y$value_y, data_frame_snake_y$value_y)
    total_sub_dataframe <- total_sub_dataframe[sample(nrow(total_sub_dataframe), nrow(total_sub_dataframe)), ]
    colnames(total_sub_dataframe) <- c("SnakeMisNewt_Pheno","Newts_Killed","Snakes_Killed")
     p <- ggplot(total_sub_dataframe) +
      #xlim(0, 1000)+
       ggtitle(title, subtitle = subt) +
       xlab(x_label) + ylab(y_label)+
       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Newts_Killed), color="Newts_Killed"), alpha=0.1)+
       geom_point(aes(x=as.numeric(SnakeMisNewt_Pheno), y=as.numeric(Snakes_Killed), color="Snakes_Killed"), alpha=0.1)+
        scale_colour_manual(name = "Species", values = c("Newts_Killed" = "darkred", "Snakes_Killed" = "steelblue"))+
        theme(plot.title = element_text(size=5)) +
        theme_bw() +  theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8))
}
  if(logy==TRUE){
    p = p + scale_y_log10()
  }
  return(p)

@@

## What About The Difference between Phenotypes??

It is possible that there might be an interaction between the phenotypes of newts and snakes and the amount of newts and snakes killed by the opposite species. To see if there might be a rough interaction I will look at the difference between the mean snake and the mean newt phenotype (snakes-newts) and the amount of individuals killed by the other species per year they  have been alive. I predict that when the phenotypess are similar there will be an equal amount of newts and snakes killed. When the phenotypes are different I will predict that the species with the higher phenotype will be killed less.

```{r, pheno difference and amount killed}

p4 <- var_by_var( Newt_mean, Snake_mean, mean_newts_eaten, mean_snakes_eaten, title="Phenotype Differences vs Individals Killed", subt="sigma = 0.2, mu = 1.5625e-10", x_label="Mean Phenotype Difference (Snake - Newt)", y_label="Species Killed by the Other Species", subtract_x=TRUE)

p4
```

This is the opposite of what I thought would occur. So much so I am triple checking the code. This figure makes it seem like there are more snakes killed the higher the snake phenotype is. Or there are less newts killed the higher the phenotype for the snake. Maybe this is an indication that newts and snakes are competing so that there are area of high resistance and areas of high toxicity which can cancel each other out but still produce a high mean phenotype? This seems very weird to me! I would need to look at the difference between individuals phenotypes based on their locations and then see where the killed values are coming from. Very strange result.
